---
title: "Data Visualization"
author: "Siliang Gong"
date: "November 21, 2021"
output: pdf_document
---


``` {r setup, include = FALSE}
library(dplyr)
library(knitr)
#library(kableExtra)
```

## Description of the data

The data used in this assignment is a Breast Cancer Coimbra data set, which is publicly available at UCI machine learning repository [(link)](https://archive.ics.uci.edu/ml/datasets/Breast+Cancer+Coimbra). The data set includes clinical features measurement for 64 patients with breast cancer and 52 healthy controls. There are 10 predictors, all quantitative, and a binary dependent variable, indicating the presence or absence of breast cancer. 

## Read the data

```{r echo = TRUE}

# read the data into a dataframe

breast.data <- read.csv("dataR2.csv")

```

## Visualization

In this section, I present the histogram of age and the scatterplot of age vs BMI.

```{r echo = TRUE}
# rename Classification to group and change group = 1 to "Healthy" and group =2 to "Patients"

breast.data = rename(breast.data, group = Classification)
breast.data$group[breast.data$group == 1] = "Healthy"
breast.data$group[breast.data$group == 2] = "Patients"

# Histogram of age

hist(breast.data$Age, xlab = "Age", main = "Histogram of Age")

# Scatterplot of Age vs BMI

plot(breast.data$Age, breast.data$BMI, xlab = "Age", ylab = "BMI", main = "Scatterplot of Age vs BMI")

```
